Variants on the Flight and Maintenance Planning problem

### 2019-03-28 latex/notes/model/model.tex
update model.

    \begin{align}
        % & m_{it'} + m_{it} \leq 1
        %   & t \in \mathcal{T}, t' \in \mathcal{T}^m_t, i \in \mathcal{I}\label{eq:rct_min}\\ 
        % & \sum_{t' \in \mathcal{T}^M_t} m_{it'} \geq  m_{it}
        %   & t \in \mathcal{T}, i \in \mathcal{I}\label{eq:rct_max}\\
        & m_{it_1t_2} = 0
          & t_1 \in \mathcal{T}^{m_{ini}}_i, t_2 \in \mathcal{T}^M_{t_1}, i \in \mathcal{I}\label{eq:rct_min_init} \\
        & \sum_{t_1 \in \mathcal{T}^{M_{ini}}_i, t_2 \in \mathcal{T}^M_{t_1} \cup \{|\mathcal{T}|\} } m_{it_1t_2} \geq  1 
          & i \in \mathcal{I}\label{eq:rct_max_init}
    \end{align}

>>>>

    \begin{align}
       % For now, we only want one or possibly two maintenances...
        & \sum_{t_1 \in \mathcal{T}, t_2 \in \mathcal{T}^M_{t_1} \cup \{|\mathcal{T}|\} } m_{it_1t_2} =  1 
          & i \in \mathcal{I}\label{eq:num_maint} \\
        % & m_{it'} + m_{it} \leq 1
        %   & t \in \mathcal{T}, t' \in \mathcal{T}^m_t, i \in \mathcal{I}\label{eq:rct_min}\\ 
        % & \sum_{t' \in \mathcal{T}^M_t} m_{it'} \geq  m_{it}
        %   & t \in \mathcal{T}, i \in \mathcal{I}\label{eq:rct_max}\\
        & m_{it_1t_2} = 0
          & t_1 \in \mathcal{T}^{m_{ini}}_i, t_2 \in \mathcal{T}^M_{t_1}, i \in \mathcal{I}\label{eq:rct_min_init} \\
        & \sum_{t_1 \in \mathcal{T}^{M_{ini}}_i, t_2 \in \mathcal{T}^M_{t_1} \cup \{|\mathcal{T}|\} } m_{it_1t_2} =  1 
          & i \in \mathcal{I}\label{eq:rct_max_init}
    \end{align}
